KidsAIR: Main analysis

### 2020-12-04 main_analysis_final.Rmd
analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 18 Nov 2020"
output: pdf_document
---

@@

@@

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT - home", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "LRTI events per child-week \n at risk compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Winter 1 = Primary model with Winter 1 data only  
ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT - home = Primary model without home as random term  
ITT outlier = Primary model with data that fixes incidence outlier

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*home_sqft_2level + 
                              child_age + 
                       (1 | cohort:area), data = analysis_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))

summary(itt_pm_results_int)

int_emtrends <- emtrends(itt_pm_results_int, home_sqft_2level ~ treatment_assigned, var = "log(pm_mean_sampling_period)")
summary(int_emtrends, conf.int = TRUE)
# This line will plot the interaction term
#emmip(itt_pm_results_int, child_age ~ treatment_assigned, cov.reduce = range)
table(model.frame(itt_pm_results_int)$treatment_assigned)
nobs(itt_pm_results_int)
```

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + filt comp", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "Difference in log(PM2.5) \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period

@@

## Model summary and diagnostic plots
```{r}
summary(er_results)
er_res <- simulateResiduals(er_results)
plot(er_res, rank = TRUE, quantreg = TRUE)
```

@@

@@

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
er_filter_comp_results <- read_rds(paste0(file_path, "Output/er_filter_comp_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_ambpm_results <- read_rds(paste0(file_path, "Output/er_ambpm_results.rds"))
er_ambtemp_results <- read_rds(paste0(file_path, "Output/er_ambtemp_results.rds"))
er_home_results <- read_rds(paste0(file_path, "Output/er_home_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_income_tidy <- results_function(er_income_results, "ER + income")
er_filter_comp_tidy <- results_function(er_filter_comp_results, "ER + filt comp")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_ambpm_tidy <- results_function(er_ambpm_results, "ER + amb PM")
er_ambtemp_tidy <- results_function(er_ambtemp_results, "ER + amb temp")
er_home_tidy <- results_function(er_home_results, "ER - home")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_income_tidy, er_filter_comp_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_ambpm_tidy, er_ambtemp_tidy, er_home_tidy)

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER + income", "ER + filt comp", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER + amb PM", "ER + amb temp", "ER - home"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI cases per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

ER + income = Primary model using income instead of education  
ER + filt comp = Primary model plus variable for filter compliance  
ER + burn level = Primary model plus self-reported burn-level compared to typical  
ER + smoke act = Primary model plus # days during sampling with smoking  
ER + window act = Primary model plus # days during sampling with windows open  
ER + door act = Primary model plus # days during sampling with doors open  
ER + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ER + amb PM = Primary model plus amb PM during LRTI at-risk period  
ER + amb temp = Primary model plus amb temp during LRTI at-risk period  
ER - home = Primary model without home as random term

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 30 Nov 2020"
output: pdf_document
---

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke

# Run primary model and print results
itt_results_int <- glmer(lrti_events_di_total ~ treatment_assigned*residents_smoke + 
                     child_age + 
                     person_time_at_risk + (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(itt_results_int, paste0(file_path, "Output/itt_results_int_age.rds"))
summary(itt_results_int)

int_emmeans <- emmeans(itt_results_int, pairwise ~ treatment_assigned | residents_smoke)
summary(int_emmeans, conf.int = TRUE)
confint(int_emmeans)

table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)
```

@@

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + filt comp",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT - home", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Primary = Logistic regression mixed model, as specified above  
ITT Winter 1 = Primary model with Winter 1 data only  
ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT - home = Primary model without home as random term  
ITT outlier = Primary model with data that fixes incidence outlier

## Analysis to assess effect modification

There were small differences in the associations across age groups (<1 vs >=1)  
and gender groups, but confidence intervals overlap substantially.  
There were minimal differences in associations across groups for levels/floors  
in the home, sqft of the home, or residents smoking.

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try home_floors_2level, home_sqft_2level, education_3level, child_age
# home_year_built_2level, stove_age_3level, stove_grade_3level, chimney_clean_3level,
# wood_collect_2level, burn_level_3level, residents_smoke

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*residents_smoke + 
                              child_age + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_pm_results_int, pairwise ~ treatment_assigned | residents_smoke)
#summary(int_emmeans, conf.int = TRUE)
confint(int_emmeans)

table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)

((exp(-.418)-1)*100)
```

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + filt comp", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

ITT Primary = Linear mixed model, as specified above  
ITT + income = Primary model plus categorical income variable  
ITT + filt comp = Primary model plus variable for filter compliance  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period

## Analysis to assess effect modification

There were small differences in the associations across groups for levels/floors,    
age of home, when chimney was cleaned, and resident smoking status,  
but confidence intervals overlap substantially.  
There were minimal differences in associations across groups for other variables.

@@

## Model summary and diagnostic plots
```{r}
summary(er_results)
er_res <- simulateResiduals(er_results)
testDispersion(er_res, alternative = "two.sided")
plot(er_res, rank = TRUE, quantreg = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try education_3level, child_age, chimney_clean_3level, wood_collect_2level, residents_smoke

# Run primary model and print results
er_results_int <- glmer.nb(lrti_events_winter ~ pm_mean_sampling_period_iqr*chimney_clean_3level + 
                          child_age + 
                          education_3level + 
                          residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk_winter), 
                          data = analysis_data_winter1)
#write_rds(er_results_int, paste0(file_path, "Output/er_results_int_age.rds"))
#summary(er_results_int)

int_emtrends <- emtrends(er_results_int, pairwise ~ chimney_clean_3level, var = "pm_mean_sampling_period_iqr")
summary(int_emtrends, conf.int = TRUE)

table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)
```

@@

er_results_lr <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 20)
write_rds(er_results_lr, paste0(file_path, "Output/er_results_lr.rds"))

@@

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_results_lr <- read_rds(paste0(file_path, "Output/er_results_lr.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
er_filter_comp_results <- read_rds(paste0(file_path, "Output/er_filter_comp_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_ambpm_results <- read_rds(paste0(file_path, "Output/er_ambpm_results.rds"))
er_ambtemp_results <- read_rds(paste0(file_path, "Output/er_ambtemp_results.rds"))
er_home_results <- read_rds(paste0(file_path, "Output/er_home_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_lr_tidy <- results_function(er_results_lr, "ER Log Reg")
er_income_tidy <- results_function(er_income_results, "ER + income")
er_filter_comp_tidy <- results_function(er_filter_comp_results, "ER + filt comp")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_ambpm_tidy <- results_function(er_ambpm_results, "ER + amb PM")
er_ambtemp_tidy <- results_function(er_ambtemp_results, "ER + amb temp")
er_home_tidy <- results_function(er_home_results, "ER - home")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_lr_tidy, er_income_tidy, er_filter_comp_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_ambpm_tidy, er_ambtemp_tidy, er_home_tidy)

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER Log Reg", "ER + income", "ER + filt comp", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER + amb PM", "ER + amb temp", "ER - home"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI events per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

ER Primary = Negative binomial mixed model, as specified above  
ER Log Reg = Logistic regression instead of Negative binomial model framework  
ER + income = Primary model using income instead of education  
ER + filt comp = Primary model plus variable for filter compliance  
ER + burn level = Primary model plus self-reported burn-level compared to typical  
ER + smoke act = Primary model plus # days during sampling with smoking  
ER + window act = Primary model plus # days during sampling with windows open  
ER + door act = Primary model plus # days during sampling with doors open  
ER + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ER + amb PM = Primary model plus amb PM during LRTI at-risk period  
ER + amb temp = Primary model plus amb temp during LRTI at-risk period  
ER - home = Primary model without home as random term

```{r, eval=FALSE, include=FALSE}
################ Plot/check individual models and various results ##############

check_model_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + moisture_closest + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)

summary(check_model_results)

# Run function to clean results
results_function <- function(model_results) {

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  #mutate(group_filter = if_else(grepl("pm_mean", term), 1, 0)) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  dplyr::select(term, estimate, conf.low, conf.high)
tidy_results

# Run results through function, save, combine for plotting
results_tidy <- results_function(check_model_results)

# Plot results
plot_estimates <- results_tidy %>%
  #filter(term != "treatment_filter_typeHoneywell") %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=1, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=1, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Results compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black")) 
plot_estimates

# Check summary data
grouped_data <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize(min(moisture_closest, na.rm = TRUE),
            median(moisture_closest, na.rm = TRUE),
            max(moisture_closest, na.rm = TRUE),
            mean(moisture_closest, na.rm = TRUE),
            sd(moisture_closest, na.rm = TRUE))
grouped_data
#table(analysis_data$moisture_closest)
#summary(analysis_data$moisture_closest)
anova_model <- lm(moisture_closest ~ treatment_assigned, data = analysis_data)
anova(anova_model)

# Check model observation numbers
table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)

# backtransform model results for log(pm) models
((exp(-.418)-1)*100)
```
